Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-11-18 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
Minor changes with regard to the use of synonyms of improvement and improve

In order to improve the number of cycles per user, we improved the
basic architecture in several different aspects.  One improvement 
involved restarting the client once the solution was
found, so that as long as the user was visiting the page it was
running an evolutionary algorithm. Another was a small algorithmic
improvement: instead of having a fixed population,
population size was randomly distributed between 128 and 256 and
different for each client.  The other improvement was the 
use the Web Worker API as described next.

JavaScript has been commonly used to develop client-side scripts
that handle the user interface, communicate asynchronously with servers and
update the content that is displayed \cite{flanagan2006javascript}.
Long-running scripts like those proposed in this work can interfere with the
responsiveness of the web application, because everything is handled by a
single thread. The Web Workers specification \cite{hickson2012web} defines an
API that allows Web developers to execute long-running scripts in parallel
with the scripts of the main page. Worker scripts are spawned in the
background allowing a thread-like operation using message-passing as the
communication mechanism between the worker's execution environment and the
main thread. According to the Web Workers W3C Candidate Recommendation
\cite{hickson2012web} workers are expected to be long-lived, they have a high
start-up performance cost, and a high per-instance memory cost. The Web Worker
API is implemented in current versions of both desktop and mobile web browsers.
For volunteer computing using the Web Worker API brings several advantages
over a single threaded implementation:

@@

A sequence diagram of the W$^2$ version of {\sf NodIO} is presented
in Figure~\ref{fig:system:w2}. In this version, clients use the Web Workers
API to run two {\sf NodEO} instances per browser. The sequence diagram shows the
interaction between processes in a time sequence. In this system there are
two kinds of asynchronous messages: HTTP Requests shown as bold arrows between
the client and the server where PUT and GET HTTP Methods are represented by
red and blue arrows respectively. There are also messages between workers and
the main thread locally in the client, these are shown as thin solid arrows.
There are three processes involved:
\begin{itemize}
\item {\em Node.js} This is the server side process which is basically
  the same as used previously, except for some minor log-related
  changes. 
\item {\em Client main thread} The main script creates
worker instances and handles the user interface.
\item {\em Worker global scope} The worker execution space does not have
access to the Document Object Model (DOM) or JQuery objects in the main thread.
Asynchronous HTTP requests to the server are implemented using the
XMLHttpRequest (XHR) object.  
\end{itemize}

>>>>

In order to improve the number of cycles per user, we enhanced the
basic architecture in several different aspects.  One improvement 
involved restarting the client once the solution was
found, so that as long as the user was visiting the page it was
running an evolutionary algorithm. Another was a small algorithmic
enhancement: instead of having a fixed population,
population size was randomly distributed between 128 and 256 and
different for each client.  The other improvement was to 
use the Web Worker API as described next.

JavaScript has been commonly used to develop client-side scripts
that handle the user interface, communicating asynchronously with servers and
updating the content that is displayed \cite{flanagan2006javascript}.
Long-running scripts like those proposed in this work can interfere with the
responsiveness of the web application, because everything is handled by a
single thread. The Web Workers specification \cite{hickson2012web} defines an
API that allows Web developers to execute long-running scripts in parallel
with the scripts of the main page. Worker scripts are spawned in the
background allowing a thread-like operation using message-passing as the
communication mechanism between the worker's execution environment and the
main thread. According to the Web Workers W3C Candidate Recommendation
\cite{hickson2012web} workers are expected to be long-lived, they have a high
start-up performance cost, and a high per-instance memory cost. The Web Worker
API is implemented in current versions of both desktop and mobile web browsers.
For volunteer computing using the Web Worker API brings several advantages
over a single threaded implementation:

@@

A sequence diagram of the W$^2$ version of {\sf NodIO} is presented
in Figure~\ref{fig:system:w2}. In this version, clients use the Web Workers
API to run two {\sf NodEO} instances per browser. The sequence diagram shows the
interaction between processes in a time sequence. In this system there are
two kinds of asynchronous messages: HTTP Requests shown as bold arrows between
the client and the server where PUT and GET HTTP Methods are represented by
red and blue arrows respectively. There are also messages between workers and
the main thread locally in the client, which are shown as thin solid arrows.
There are three processes involved:
\begin{itemize}
\item {\em Node.js} This is the server side process which is basically
  the same as used previously, except for some minor log-related
  changes. 
\item {\em Client main thread} The main script creates
worker instances and handles the user interface.
\item {\em Worker global scope} The worker execution space does not have
access to the Document Object Model (DOM) or JQuery objects in the main thread.
Asynchronous HTTP requests to the server are implemented using the
XMLHttpRequest (XHR) object.  
\end{itemize}
